
---
title: "Overview of all experiment - New Probes"
subtitle: 'Overview all experiments - New Probes.Rmd'
fontfamily: sans
output:
  pdf_document:
    toc: yes
    toc_depth: 3
  html_document: default
  word_document: default
---

```{r Libraries, echo=FALSE, warning=FALSE, message=FALSE}

library(tidyverse)
library(readxl)
library(knitr)
library(ggsignif)
library(gridExtra)
library(kableExtra)

options(digits=2)

```


```{r Source, echo=FALSE, message=FALSE}

# Read in data

source('../Utility Code/Read Data - New Probes - Traditional.r')
source('../Utility Code/Colours.r')

```


```{r , echo=FALSE}

data_file_new_30_02 <- '../../Data Integrated/Paint New Probes - 30 squares - 2 DR'
data_file_new_30_05 <- '../../Data Integrated/Paint New Probes - 30 squares - 5 DR'
data_file_new_30_10 <- '../../Data Integrated/Paint New Probes - 30 squares - 10 DR'
data_file_new_30_30 <- '../../Data Integrated/Paint New Probes - 30 squares - 30 DR'

data_file_new_20_02 <- '../../Data Integrated/Paint New Probes - 20 squares - 2 DR'
data_file_new_20_05 <- '../../Data Integrated/Paint New Probes - 20 squares - 5 DR'
data_file_new_20_10 <- '../../Data Integrated/Paint New Probes - 20 squares - 10 DR'
data_file_new_20_30 <- '../../Data Integrated/Paint New Probes - 20 squares - 30 DR'

data_file <- data_file_new_30_02   # Original
data_file <- data_file_new_20_05
manually_exclude <- FALSE
duration_exclude <- TRUE
```


```{r , echo=FALSE}

data <- read_data(data_file, 'Output', manually_exclude=manually_exclude, duration_exclude=duration_exclude)

squares_master <- data$squares_master
images_master  <- data$images_master

```


\newpage

# Summary

## All Cell Types, Probe Types and Adjuvants, ignoring Concentration and Threshold

```{r, Overview 1, echo = FALSE, message=FALSE}

experiment_overview <- squares_master %>% 
  group_by(Cell_Type, Adjuvant, Probe,  ) %>% 
  summarise(Nr_Exps    = n_distinct(Experiment_Name), 
            Nr_Images  = n_distinct(Recording_Name), 
            Nr_Squares = n(), 
            .groups = 'keep') 

experiment_overview$Squares_Images_Ratio <- round(experiment_overview$Nr_Squares / experiment_overview$Nr_Images, digits = 0)

kable(experiment_overview, col.names = c('C Type',
                                         'Adj',
                                         'Probe',
                                         'Nr Exp',
                                         'Nr Imgs',
                                         'Nr Sqs',
                                         'Sqs/Imgs')) 
# write_csv(experiment_overview, '~/Downloads/Thesis Experiments - Summary - Ignoring Concentration and Threshold.csv')

```

\newpage

## All Cell Types, Probe Types and Adjuvants, separate Concentration and Threshold 


```{r, Overview 2, echo=FALSE, message=FALSE, error=FALSE}
experiment_overview <- squares_master %>% 
  group_by(Cell_Type, Probe_Type, Probe, Adjuvant, Concentration, Threshold) %>% 
  summarise(Nr_Exps              = n_distinct(Experiment_Name), 
            Nr_Images            = n_distinct(Recording_Name), 
            Nr_Squares           = n(), 
            Squares_Images_Ratio = n(),
            .groups              = 'keep') 

experiment_overview$Squares_Images_Ratio <- round(experiment_overview$Nr_Squares / experiment_overview$Nr_Images, digits = 0)

kable(experiment_overview, col.names = c('CT',
                                         'PT',
                                         'Probe',
                                         'Adj',
                                         'Conc',
                                         'Thresh',
                                         'Nr Exp',
                                         'Nr Imgs',
                                         'Nr Sqs',
                                         'Sqs/Imgs'))
# write_csv(experiment_overview, '~/Downloads/Thesis Experiments - Summary - Separate Concentration and Threshold.csv')

```

\newpage

## Experiments with unusual thresholds (> 20)

```{r, echo = FALSE, eval=FALSE, message=FALSE}

images_master %>% 
  select(Experiment_Date, Experiment_Nr, Experiment_Seq_Nr, Cell_Type, Adjuvant, Probe_Type, Probe, Threshold, Nr_Visible_Squares) %>%
  filter(Threshold > 20) %>% 
  kable(col.names = c('Experiment Date',
                      'Exp Nr',
                      'Exp Seq Nr',
                      'Cell Type',
                      'Adjuvant',
                      'Probe Type',
                      'Probe Name',
                      'Threshold',
                      'Nr Visible Squares'))
```



\newpage

## Experiments where no visible square is present

```{r, no_visible_squares, echo = FALSE, message=FALSE}

images_master %>% 
  select(Experiment_Date, Experiment_Nr, Experiment_Seq_Nr, Cell_Type, Adjuvant, Probe_Type, Probe, Nr_Visible_Squares) %>%
  filter(Nr_Visible_Squares == 0) %>% 
  select(-Nr_Visible_Squares) %>% 
  kable(col.names = c('Experiment Date',
                      'Exp Nr',
                      'Exp Seq Nr',
                      'Cell Type',
                      'Adjuvant',
                      'Probe Type',
                      'Probe Name'))
```

\newpage

## Experiments that were excluded

```{r, rejected, echo = FALSE, message=FALSE}

images_master %>% 
  select(Experiment_Date, Experiment_Nr, Experiment_Seq_Nr, Cell_Type, Probe_Type, Probe, Exclude) %>%
  filter(Exclude == TRUE) %>% 
  select(-Exclude) %>% 
  kable(col.names = c('Experiment Date',
                      'Exp Nr',
                      'Exp Seq Nr',
                      'Cell Type',
                      'Probe Type',
                      'Probe Name'))


```


\newpage

## Concentrations at which experiments have been done

```{r, echo = FALSE, message = FALSE}
squares_master %>% 

  group_by(Cell_Type, Probe_Type, Concentration) %>% 
  summarise(Nr_Squares=n(), .groups = 'keep') %>% 
  kable(col.names = c('Cell Type',
                      'Probe Type',
                      'Concentration',
                      'Nr of Squares'))
```


\newpage

## Thresholds at which experiments have been done - Number Squares

```{r, echo = FALSE, message = FALSE}
bar_data <- squares_master %>% 
  group_by(Cell_Type, Adjuvant, Probe_Type, Probe, Threshold) %>% 
  summarise(Nr_Squares=n(), .groups = 'keep') 


bar_data%>% 
  kable(col.names = c('Cell Type',
                      'Adjuvant',
                      'Probe Type',
                      'Probe',
                      'Threshold',
                      'Nr of Squares'))
```

\newpage

## Thresholds at which experiments have been done - Number Images

```{r, echo = FALSE, message = FALSE}
bar_data <- images_master %>% 
  group_by(Cell_Type, Adjuvant, Probe_Type, Threshold) %>% 
  summarise(Nr_Images=n(), .groups = 'keep') 


bar_data%>% 
  kable(col.names = c('Cell Type',
                      'Adjuvant',
                      'Probe Type',
                      'Threshold',
                      'Nr of Images'))
```


\newpage

## Threshold distribution'

```{r, echo=FALSE, message=FALSE, error=FALSE}

bar_data$Threshold <- as.factor(bar_data$Threshold )
bar_data %>% 
  ggplot() +
    geom_col(aes(x=Cell_Type, y=Nr_Images, fill=Threshold, group=Threshold), 
             width=0.5,
             position = position_dodge2(preserve = 'single')) +
    geom_text(aes(x     = Cell_Type, 
                  y     = Nr_Images, 
                  label = Nr_Images, 
                  group = Threshold),
              position = position_dodge(width = 0.5),
              vjust = -0.5, 
              size = 2) 
```


\newpage

## Experiments for specified Cell Type and Thresholds at which experiments have been done - Number Images

```{r, echo = FALSE, message = FALSE}

bar_data   <- images_master %>% 
  group_by(Experiment_Date, Cell_Type, Probe_Type, Threshold) %>% 
  summarise(Nr_Images=n(), .groups = 'keep') 


bar_data%>% 
  kable(col.names = c('Experiment Date',
                      'Cell Type',
                      'Probe Type',
                      'Threshold',
                      'Nr of Images'))
```

\newpage

# Tau 


## Tau for Cell Type, Probe Type and Probe, ignoring differences in Concentration and Threshold 


```{r, echo=FALSE, message=FALSE, error=FALSE}
experiment_overview <- squares_master %>% 
  group_by(Cell_Type, Probe_Type, Probe, Adjuvant) %>% 
  summarise(Nr_Exps        = n_distinct(Experiment_Name), 
            Nr_Images      = n_distinct(Recording_Name), 
            Nr_Squares     = n(),
            Squares_Images_Ratio = n(),
            Median_Tau     = round(median(Tau), 0),
            Median_Density = round(median(Density), 0),
            .groups = 'keep') 

experiment_overview$Squares_Images_Ratio <- round(experiment_overview$Nr_Squares / experiment_overview$Nr_Images, digits = 0)

kable(experiment_overview, col.names = c('CT',
                                         'PT',
                                         'Probe',
                                         'Adj',
                                         'NrExp',
                                         'NrImgs',
                                         'NrSqs',
                                         'Sqs/Imgs',
                                         'Tau',
                                         'Density')) %>% 
  column_spec(3, width='4em')

# write_csv(experiment_overview, '~/Downloads/Thesis Experiments - Tau and Density - Ignoring Concentration and Threshold.csv')
```

\newpage


## Tau of probes without Adjuvant

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=8, fig.width=12}


tau_data <- squares_master  %>% 
  filter(Cell_Type=='BMDM') %>% 
  filter(Tau > 0)

meds <- tau_data %>% 
  group_by(Cell_Type, Probe_Type, Probe, Adjuvant) %>%
  summarize(med = round(median(Density), 0), .groups = 'keep')

ggplot(data=tau_data, aes(x=Probe, y = Density)) + 
  geom_boxplot(width = 0.5, show.legend = FALSE) +
  #geom_jitter(width=0.2) +
  #geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
  geom_text(data = meds, aes(y = med, label = round(med, 2)), size = 3, vjust = -0.5, color = "black") +
  geom_text(aes(label=paste0("n = ", after_stat(count))), y = 0, stat = 'count', colour = "black", size = 3) +  
  labs(x = '', 
       y = 'Average residence time (ms)',
       caption = '') +
  scale_y_continuous(limits = c(0, 100), breaks=seq(0, 400, 100)) +
  theme_light(base_size = 16) +
  theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
    facet_wrap(Cell_Type ~ Adjuvant, drop = TRUE)
```


\newpage

## Tau of probes with LPS

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=8, fig.width=12}


tau_data <- squares_master  %>% 
  filter(Cell_Type =='BMDC') %>% 
  filter(Tau > 0)

meds <- tau_data %>% 
  group_by(Probe, Cell_Type) %>%
  summarize(med = round(median(Tau), 0), .groups = 'keep')

tau_data %>%
  ggplot(aes(x=Probe, y = Tau)) + 
    geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
    # geom_boxplot(width = 0.5, show.legend = FALSE) +
    # geom_jitter(width=0.2) +
    geom_text(data = meds, aes(y = med, label = round(med, 2)), size = 3, vjust = -0.5, color = "black") +
    geom_text(aes(label=paste0("n = ", after_stat(count))), y = 0, stat = 'count', colour = "black", size = 3) +  
    labs(x = '', 
         y = 'Average residence time (ms)',
         caption = '') +
    scale_y_continuous(limits = c(0, 350), breaks=seq(0, 3500, 100)) +
    theme_light(base_size = 16) +
    theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
      facet_wrap(Cell_Type ~ Adjuvant, drop = TRUE)

```

\newpage

## Tau of probes with IL-4

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=8, fig.width=12}


tau_data <- squares_master  %>% 
  filter(Adjuvant=='IL-4') %>% 
  filter(Tau > 0)

meds <- tau_data %>% 
  group_by(Probe, Cell_Type) %>%
  summarize(med = round(median(Tau), 0), .groups = 'keep')

tau_data %>%
  ggplot(aes(x=Probe, y = Tau)) + 
    geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
    # geom_boxplot(width = 0.5, show.legend = FALSE) +
    # geom_jitter(width=0.2) +
    geom_text(data = meds, aes(y = med, label = round(med, 2)), size = 3, vjust = -0.5, color = "black") +
    geom_text(aes(label=paste0("n = ", after_stat(count))), y = 0, stat = 'count', colour = "black", size = 3) +  
    labs(x = '', 
         y = 'Average residence time (ms)',
         caption = '') +
    scale_y_continuous(limits = c(0, 350), breaks=seq(0, 3500, 100)) +
    theme_light(base_size = 16) +
    theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
      facet_wrap( ~ Cell_Type, drop = TRUE)

```


\newpage

## Tau of probes on BMDM

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=8, fig.width=12}


tau_data <- squares_master  %>% 
  filter(Cell_Type=='BMDM') %>% 
  filter(Tau > 0)

meds <- tau_data %>% 
  group_by(Probe, Cell_Type, Adjuvant) %>%
  summarize(med = round(median(Tau), 0), .groups = 'keep')

tau_data %>%
  ggplot(aes(x=Probe, y = Tau)) + 
    geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
    # geom_boxplot(width = 0.5, show.legend = FALSE) +
    # geom_jitter(width=0.2) +
    geom_text(data = meds, aes(y = med, label = round(med, 2)), size = 3, vjust = -0.5, color = "black") +
    geom_text(aes(label=paste0("n = ", after_stat(count))), y = 0, stat = 'count', colour = "black", size = 3) +  
    labs(x = '', 
         y = 'Average residence time (ms)',
         caption = '') +
    scale_y_continuous(limits = c(0, 400), breaks=seq(0, 400, 100)) +
    theme_light(base_size = 16) +
    theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
      facet_wrap( ~ Adjuvant, drop = TRUE)

```
\newpage

# Density

## Density for Cell Type, Probe Type and Probe, ignoring differences in Concentration and Threshold 


```{r, echo=FALSE, message=FALSE, error=FALSE}

experiment_overview <- squares_master %>% 
  group_by(Cell_Type, Probe_Type, Adjuvant, Probe, ) %>% 
  summarise(Nr_Exps              = n_distinct(Experiment_Name), 
            Nr_Images            = n_distinct(Recording_Name), 
            Nr_Squares           = n(),
            Squares_Images_Ratio = n(),
            Median_Density       = round(median(Density), 1),
            .groups = 'keep') 

experiment_overview$Squares_Images_Ratio <- round(experiment_overview$Nr_Squares / experiment_overview$Nr_Images, digits = 0)

kable(experiment_overview, col.names = c('CT',
                                         'PT',
                                         'Adj',
                                         'Probe',
                                         'NrExp',
                                         'NrImgs',
                                         'NrSqs',
                                         'Sqs/Imgs',
                                         'Density')) 

# write_csv(experiment_overview, '~/Downloads/Thesis Experiments - Tau and Density - Ignoring Concentration and Threshold.csv')
```


\newpage

## Density for Cell Type, Probe Type, Probe, Concentration and Threshold  


```{r, Overview 4, echo=FALSE, message=FALSE, error=FALSE}
experiment_overview <- squares_master %>% 
  group_by(Cell_Type, Probe_Type, Probe, Adjuvant, Concentration, Threshold) %>% 
  summarise(Nr_Exps        = n_distinct(Experiment_Name), 
            Nr_Images      = n_distinct(Recording_Name), 
            Nr_Squares     = n(),
            Squares_Images_Ratio = n(),
            Median_Density = round(median(Density), 0),
            .groups = 'keep') 

experiment_overview$Squares_Images_Ratio <- round(experiment_overview$Nr_Squares / experiment_overview$Nr_Images, digits = 0)

kable(experiment_overview, col.names = c('CT',
                                         'PT',
                                         'Probe',
                                         'Adj',
                                         'Conc',
                                         'Thresh',
                                         'NrExp',
                                         'NrImgs',
                                         'NrSqs',
                                         'Sqs/Imgs',
                                         'Density')) %>% 
  column_spec(4, width ="3em")


# write_csv(experiment_overview, '~/Downloads/Thesis Experiments - Tau and Density - Separate Concentration and Threshold.csv')
```




