---
title: "BMDC and CHO-MR with Epitope and Simple probes no Adjuvant"
subtitle: 'BMDC and CHO-MR - Simple and Epitope - None - Regular Probes - Traditional.Rmd'
fontfamily: sans
output:
  pdf_document:
    toc: yes
    toc_depth: 3
  html_document: default
  word_document: default
  editor_options: 
  chunk_output_type: inline
---

```{r Libraries, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(knitr)
library(ggsignif)
library(gridExtra)

options(digits=22)

```


```{r, significance, echo=FALSE}

source('../Utility Code/Significance.R')
source('../Utility Code/Read Data - Regular Probes - Traditional.R')
source('../Utility Code/Colours.R')

```


```{r , echo=FALSE}

data_file_regular_20_02 <- '../../Data - v5/Paint Regular Probes - 20 squares - 2 DR'
data_file_regular_20_05 <- '../../Data Integrated - v2/Paint Regular Probes - 20 squares - 5 DR'
data_file_regular_20_10 <- '../../Data Integrated - v2/Paint Regular Probes - 20 squares - 10 DR'
data_file_regular_20_30 <- '../../Data Integrated - v2/Paint Regular Probes - 20 squares - 30 DR'

data_file_regular_30_02 <- '../../Data Integrated - v2/Paint Regular Probes - 30 squares - 2 DR'
data_file_regular_30_05 <- '../../Data Integrated - v2/Paint Regular Probes - 30 squares - 5 DR'
data_file_regular_30_10 <- '../../Data Integrated - v2/Paint Regular Probes - 30 squares - 10 DR'
data_file_regular_30_30 <- '../../Data Integrated - v2/Paint Regular Probes - 30 squares - 30 DR'

data_file <- data_file_regular_20_02
manually_exclude <- FALSE
duration_exclude <- TRUE

```


```{r , echo=FALSE}

data <- read_data(data_file, 'Output', manually_exclude=manually_exclude, duration_exclude=duration_exclude)

squares_master <- data$squares_master
images_master  <- data$images_master

```




\newpage

# Significance of Tau results

## CHO-MR - Simple - None
```{r, echo=FALSE}
td <- squares_master %>% 
  filter(Cell_Type  ==   'CHOMR') %>% 
  filter(Probe_Type ==   'Simple') %>% 
  filter(Structure  %in% c('Mono', 'Tri', 'Control')) %>% 
  filter(Adjuvant   ==   'None')

significance_tau <- create_tau_significance_table(td) 

significance_tau %>% 
   kable(row.names = FALSE)
```

## CHO-MR - Epitope - None

```{r, echo=FALSE}

td <- squares_master %>% 
  filter(Cell_Type   ==   'CHOMR') %>% 
  filter(Probe_Type  ==   'Epitope') %>% 
  filter(Structure   %in%  c('Mono', 'Tri', 'Control')) %>% 
  filter(Adjuvant    ==   'None')

significance_tau <- create_tau_significance_table(td) 

significance_tau %>% 
   kable(row.names = FALSE)
```

\newpage

# Tau of probes on CHO-MR and BMDC

Here the simple and epitope probes on CHO-MRE and BMDC are shown

```{r echo=FALSE, tau, fig.fullwidth=TRUE, fig.height=12, fig.width=12}


tau_data <- squares_master %>% 
  filter(Cell_Type  %in% c('CHOMR', 'BMDC')) %>%
  filter(Probe_Type %in% c('Simple')) %>%    
  filter(Probe  %in% c('1 Mono', '2 Tri', '6 Tri')) 

meds <- tau_data %>% 
  group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
  summarize(med = round(median(Tau), 0), .groups = 'keep')


ggplot(data = tau_data, aes(x=Probe, y = Tau, fill = Structure)) + 
    # geom_violin(width = 0.5, show.legend = FALSE) +
    geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
    geom_text(data = meds, aes(y = med, label = round(med, 2)), size = 3, vjust = -0.5, color = "black") +
    geom_text(aes(label=paste0("n = ", after_stat(count))), y = 0, stat = 'count', colour = "black", size = 3) +  
    labs(x = '', 
         y = 'Average residence time (ms)',
         caption = '') +
    scale_y_continuous(limits = c(0, 600), breaks=seq(0, 600, 100)) +
    scale_fill_manual(values=c(green_mono,
                               green_tri,
                               green_control)) +
    theme_light(base_size = 16) +
    theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
      facet_grid(Cell_Type ~ Probe_Type, drop = TRUE)


```

\newpage

# Tau of probes on CHO-MR and BMDC with significance indicated

Here the simple and epitope probes on CHO-MRE and BMDC are shown

```{r echo=FALSE, tau_significance_box, fig.fullwidth=TRUE, fig.height=10, fig.width=12}

generate_tau_significance <- function(plot_data, y_limit, grid) {


  significance_tau <- create_tau_significance_table(plot_data)
  
  # Specify which pairs of probes you want to compare
  signif = list(c('1 Mono', '2 Mono'),
                c('2 Mono', '6 Mono'),
                c('1 Mono', '6 Mono'),
                c('1 Tri', '2 Tri'),
                c('2 Tri', '6 Tri'),
                c('1 Tri', '6 Tri'))
  
  # Retrieve the previously calculated significance for these pairs
  
  signif_value  <- c(get_significance(significance_tau, '1 Mono', '2 Mono'),
                     get_significance(significance_tau, '2 Mono', '6 Mono'),
                     get_significance(significance_tau, '1 Mono', '6 Mono'),
                     get_significance(significance_tau, '1 Tri',  '2 Tri'),
                     get_significance(significance_tau, '2 Tri',  '6 Tri'),
                     get_significance(significance_tau, '1 Tri',  '6 Tri'))
  
  
  signif_num = as.numeric(signif_value)
  for ( i in 1:length(signif_value)) {
    if (signif_num[i] > 0.05) {
      signif_value[i] = 'NS'
    }
  }

  
  meds <- plot_data %>% 
    group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
    summarize(med = round(median(Tau), 0), .groups = 'keep')
  
  plot <- plot_data %>%
    ggplot(aes(x=Probe, y = Tau, fill = Structure)) + 
      # geom_boxplot(width = 0.9, outlier.shape = NA, show.legend = FALSE) +
      geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
      geom_signif(comparisons = signif, annotations = signif_value, y_position = 450, step_increase = 0.2) +
      geom_text(data = meds, aes(y = med, label = round(med, 2)), size = 3, vjust = -0.5, color = "black") +
      geom_text(aes(label=paste0("n = ", after_stat(count))), y = 0, stat = 'count', colour = "black", size = 3) +  
      labs(x = '', 
           y = 'Average residence time (ms)',
           caption = '') +
      # scale_y_continuous(limits = c(0, y_limit), breaks=seq(0, y_limit, 200)) +
      scale_fill_manual(values=c(green_mono,
                                 green_tri,
                                 green_control)) +
      theme_light(base_size = 16) +
      theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
      if (grid == TRUE) {
        facet_grid(Cell_Type ~ Probe_Type, drop = TRUE)
      }
      else {
        facet_wrap( ~ Probe_Type, drop = TRUE)
      }
   return (plot)
   
}

```


### Tau and density plots for CHO-MR simple probes in 1figure
```{r echo=FALSE, tau_significance_box, fig.fullwidth=TRUE, fig.height=10, fig.width=12}

generate_tau_significance <- function(plot_data, y_limit, grid) {


  significance_tau <- create_tau_significance_table(plot_data)
  
  # Specify which pairs of probes you want to compare
  signif = list(c('1 Mono', '2 Mono'),
                c('2 Mono', '6 Mono'),
                c('1 Mono', '6 Mono'),
                c('1 Tri', '2 Tri'),
                c('2 Tri', '6 Tri'),
                c('1 Tri', '6 Tri'))
  
  # Retrieve the previously calculated significance for these pairs
  
  signif_value  <- c(get_significance(significance_tau, '1 Mono', '2 Mono'),
                     get_significance(significance_tau, '2 Mono', '6 Mono'),
                     get_significance(significance_tau, '1 Mono', '6 Mono'),
                     get_significance(significance_tau, '1 Tri',  '2 Tri'),
                     get_significance(significance_tau, '2 Tri',  '6 Tri'),
                     get_significance(significance_tau, '1 Tri',  '6 Tri'))
  
  
  signif_num = as.numeric(signif_value)
  for ( i in 1:length(signif_value)) {
    if (signif_num[i] > 0.05) {
      signif_value[i] = 'NS'
    }
  }

  
  meds <- plot_data %>% 
    group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
    summarize(med = round(median(Tau), 0), .groups = 'keep')
  
  plot <- plot_data %>%
    ggplot(aes(x=Probe, y = Tau, fill = Structure)) + 
      # geom_boxplot(width = 0.9, outlier.shape = NA, show.legend = FALSE) +
      geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
      geom_signif(comparisons = signif, annotations = signif_value, y_position = 450, step_increase = 0.2) +
      geom_text(data = meds, aes(y = med, label = round(med, 2)), size = 3, vjust = -0.5, color = "black") +
      geom_text(aes(label=paste0("n = ", after_stat(count))), y = 0, stat = 'count', colour = "black", size = 3) +  
      labs(x = '', 
           y = 'Average residence time (ms)',
           caption = '') +
      # scale_y_continuous(limits = c(0, y_limit), breaks=seq(0, y_limit, 200)) +
      scale_fill_manual(values=c(green_mono,
                                 green_tri,
                                 green_control)) +
      theme_light(base_size = 16) +
      theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
      if (grid == TRUE) {
        facet_grid(Cell_Type ~ Probe_Type, drop = TRUE)
      }
      else {
        facet_wrap( ~ Probe_Type, drop = TRUE)
      }
   return (plot)
   
}

```

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=10, fig.width=12}

# Filter the data once
td <- squares_master %>%
  filter(Probe_Type %in% c('Simple', 'Epitope'),
         Structure  %in% c('Mono', 'Tri', 'Control'),
         Adjuvant == 'None')

# Function to generate and customize the plot
generate_and_customize_plot <- function(cell_type, probe_type, y_limit, customize_y_axis = FALSE) {
  plot_data <- td %>%
    filter(Cell_Type == cell_type, Probe_Type == probe_type)
  
  plot <- generate_tau_significance(plot_data, y_limit, customize_y_axis)
  
  if (customize_y_axis) {
    plot <- plot +
      theme(axis.text.y = element_blank(),
            axis.ticks.y = element_blank(),
            axis.line.y = element_blank(),
            panel.border = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.line = element_line(colour = "black")) +
      labs(x = '', y = '', caption = '')
  }
  
  return(plot)
}

# Generate the plots
p1 <- generate_and_customize_plot('CHOMR', 'Simple', 800, FALSE)
p2 <- generate_and_customize_plot('CHOMR', 'Epitope', 800, TRUE)
p3 <- generate_and_customize_plot('BMDC', 'Simple', 800, FALSE)
p4 <- generate_and_customize_plot('BMDC', 'Epitope', 800, TRUE)

# Combine the plots in a grid
grid.arrange(p1, p2, p3, p4, ncol = 2)

```


