---
title: "Tau of Epitope probes on CHO-MR and BMDC"
subtitle: 'CHO-MR and BMDC - Epitope.Rmd'
fontfamily: sans
output:
  pdf_document:
    toc: yes
    toc_depth: 3
  html_document: default
  word_document: default
---

```{r Libraries, echo=FALSE, warning=FALSE, message=FALSE}

library(tidyverse)
library(readxl)
library(knitr)
library(ggsignif)
library(gridExtra)
library(ggtext)

```


```{r Source, echo=FALSE, message=FALSE}

source('../Utility Code/Read Data - Regular Probes - Traditional.R')
source('../Utility Code/Colours.r')
source('../Utility Code/Significance.R')

```

```{r , echo=FALSE}

data_file_regular_20_02 <- '../../Data Integrated/Paint Regular Probes - 20 squares - 2 DR'
data_file_regular_20_05 <- '../../Data Integrated/Paint Regular Probes - 20 squares - 5 DR'
data_file_regular_20_10 <- '../../Data Integrated/Paint Regular Probes - 20 squares - 10 DR'
data_file_regular_20_30 <- '../../Data Integrated/Paint Regular Probes - 20 squares - 30 DR'

data_file_regular_30_02 <- '../../Data Integrated/Paint Regular Probes - 30 squares - 2 DR'
data_file_regular_30_05 <- '../../Data Integrated/Paint Regular Probes - 30 squares - 5 DR'
data_file_regular_30_10 <- '../../Data Integrated/Paint Regular Probes - 30 squares - 10 DR'
data_file_regular_30_30 <- '../../Data Integrated/Paint Regular Probes - 30 squares - 30 DR'

data_file <- data_file_regular_20_02
manually_exclude <- FALSE
duration_exclude <- TRUE

```


```{r , echo=FALSE}

data <- read_data(data_file, 'Output', manually_exclude=manually_exclude, duration_exclude=duration_exclude)

squares_master <- data$squares_master
images_master  <- data$images_master

```


\newpage

# Tau of Epitope probes on CHO-MR and BMDC

Description of the figure:

* Cell types:         CHO-MR and BMDC
* Probe type:         Epitope
* Adjuvant:           None

For Tau it is ok to take all concentrations and all quality threshold values

\hfill\break
\hfill\break


```{r echo=FALSE}
generate_labels <- function(label_names, label_numbers) {
  # Check that label_names and label_numbers are of the same length
  if (length(label_names) != length(label_numbers)) {
    stop("label_names and label_numbers must have the same length.")
  }
  
  # Create formatted labels with bold numbers
  formatted_labels <- paste0(label_names, "(<b>", label_numbers, "</b>)")
  
  return(formatted_labels)
}

# Define the label names and corresponding numbers
label_names <- c('1 Mono', '2 Mono', '6 Mono', '1 Tri', '2 Tri', '6 Tri', 'Control')
label_numbers <- c(1, 2, 3, 4, 5, 6, 7)

# Generate the labels
formatted_labels <- generate_labels(label_names, label_numbers)

```

```{r echo=FALSE, tau_significance_violin}

generate_tau_plot <- function(tau_table, y_limit) {
  
  # Check if the tau_table has the required columns
  required_columns <- c("Probe", "Cell_Type", "Probe_Type", "Structure", "Tau")
  if (!all(required_columns %in% colnames(tau_table))) {
    stop("tau_table must contain the following columns: Probe, Cell_Type, Probe_Type, Structure, and Tau.")
  }
  
  # Create the significance table
  significance_tau <- create_tau_significance_table(tau_table)
  
  # Specify which pairs of probes to compare
  signif <- list(c('1 Mono', '2 Mono'),
                 c('2 Mono', '6 Mono'),
                 c('1 Mono', '6 Mono'),
                 c('1 Tri', '2 Tri'),
                 c('2 Tri', '6 Tri'),
                 c('1 Tri', '6 Tri'))

  
  # Retrieve the significance values for these pairs
  signif_value <- sapply(signif, function(x) get_significance(significance_tau, x[1], x[2]))
  
  # Change to significance levels with stars
  signif_num = as.numeric(signif_value)
  for (i in 1:length(signif_value)) { 
    if (signif_num[i] > 0.05) {
      signif_value[i] = 'NS'
    } else if (signif_num[i] > 0.01) {
      signif_value[i] = '*'
    }
    else if (signif_num[i] > 0.001) {
      signif_value[i] = '**'
    }
    else if (signif_num[i] > 0.0001) {
       signif_value[i] = '***'
    }
    else {
      signif_value[i] = '****'
    }  
  }

  # Calculate median values for each group
  meds <- tau_table %>% 
    group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
    summarize(med = round(median(Tau), 0), .groups = 'keep')

  # Define text size
  basesize <- 8

  # Generate the plot
  plot_data <- ggplot(tau_table, aes(x = Probe, y = Tau, fill = Structure)) + 
    geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale = 'width') +
    geom_signif(comparisons = signif, annotations = signif_value, 
                y_position = 450, step_increase = 0.1, textsize = 3) +
    geom_text(data = meds, aes(y = med, label = med), 
              size = 4, vjust = -0.5, color = "black") +
    geom_text(aes(label = paste0("n = ", after_stat(count))), 
              y = -8, stat = 'count', color = "black", size = 3) + 
    labs(x = '', 
         y = 'Average residence time (ms)',
         caption = '') +
    scale_y_continuous(limits = c(-10, y_limit), breaks = seq(0, y_limit, 200)) +
    scale_fill_manual(values = c(green_mono, green_tri, green_control)) +
    theme_light(base_size = basesize) +
    theme(panel.border = element_blank(), 
          panel.grid.minor = element_blank(), 
          axis.line = element_line(colour = "black")) +
    theme(text = element_text(size = basesize), 
          axis.text = element_text(size = basesize), 
          axis.title = element_text(size = basesize))

  return(plot_data)
}

```


\newpage

# Figure 4d - Tau CHO-MR - Epitope - None

```{r echo=FALSE, fig.fullwidth=TRUE, fig.width=6, fig.height=4 }

# ----------------------------------------------------------------------------
# For Tau it is ok to take all concentrations and all quality threshold values
# ----------------------------------------------------------------------------

# Generate the CHO-MR plot 
tau_table <- squares_master  %>% 
  filter(Cell_Type  == 'CHOMR',
         Probe_Type == 'Epitope',
         Adjuvant   == 'None')
p_cho <- generate_tau_plot (tau_table, 800)

p_cho +
  scale_x_discrete(labels = formatted_labels) +
  theme(axis.text.x = element_markdown(size = 9))

ggsave("./Figures/Traditional/Figure 4d.png", width = 6, height=4)

```


\newpage

# Figure 4e - Tau BMDC - Epitope - None

```{r echo=FALSE, fig.fullwidth=TRUE, fig.width=6, fig.height=4}
# Generate the BMDC plot 
tau_table <- squares_master  %>% 
  filter(Cell_Type  == 'BMDC',
         Probe_Type == 'Epitope',
         Adjuvant   == 'None')
p_bmdc <- generate_tau_plot (tau_table, 800)

p_bmdc +
  scale_x_discrete(labels = formatted_labels) +
  theme(axis.text.x = element_markdown(size = 9))

ggsave("./Figures/Traditional/Figure 4e.png", width=6, height=4)

```




\newpage

# Figure 4f  - Density CHO-MR, Epitope, Concentration 5, Threshold 5


```{r echo=FALSE, fig.fullwidth=TRUE, fig.width=6, fig.height=4 }

density_table <- squares_master%>% 
  filter(Cell_Type     == 'CHOMR',
         Probe_Type    == 'Epitope',
         Concentration == 5,
         Adjuvant      == 'None',
         Threshold     == 5)

y_max         <- 120
y_ticks       <- 20

# Create the significance table
significance_cho_epitope_5 <- create_density_significance_table(density_table)

# Specify which pairs of probes to compare
signif <- list(c('1 Mono', '2 Mono'),
               c('2 Mono', '6 Mono'),
               c('1 Mono', '6 Mono'),
               c('1 Tri', '2 Tri'),
               c('2 Tri', '6 Tri'),
               c('1 Tri', '6 Tri'))

# Retrieve the significance values for these pairs
signif_value <- sapply(signif, function(x) get_significance(significance_cho_epitope_5, x[1], x[2]))

# Change to significance levels with stars
signif_num = as.numeric(signif_value)
for (i in 1:length(signif_value)) { 
  if (signif_num[i] > 0.05) {
    signif_value[i] = 'NS'
  } else if (signif_num[i] > 0.01) {
    signif_value[i] = '*'
  }
  else if (signif_num[i] > 0.001) {
    signif_value[i] = '**'
  }
  else if (signif_num[i] > 0.0001) {
     signif_value[i] = '***'
  }
  else {
    signif_value[i] = '****'
  }  
}


meds <- density_table %>% 
  group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
  summarize(med = round(median(Density), 1), .groups = 'keep')

cho_mr_density <- density_table %>%
  ggplot(aes(x=Probe, y = Density, fill = Structure)) +
    geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
    geom_signif(comparisons = signif, annotations = signif_value, y_position = 65, step_increase = 0.2, textsize = 3) +
    geom_text(data = meds, aes(y = med, label = round(med, 1)), size = 3, vjust = -0.5, color = "black") +
    geom_text(aes(label=paste0("n = ", after_stat(count))), y = -2, stat = 'count', colour = "black", size = 3) +
    labs(x = '',
         y = expression(events  / microm^2  /  sec (x1000))) +
    scale_y_continuous(limits = c(0, y_max), breaks=seq(0, y_max, y_ticks)) +
    scale_fill_manual(values=c(green_mono,
                               green_tri,
                               green_control)) +
    theme_light(base_size = 12) +
    theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))


cho_mr_density +
  scale_x_discrete(labels = formatted_labels) +
  theme(axis.text.x = element_markdown(size = 9))


ggsave("./Figures/Traditional/Figure 4f.png", width = 6, height=4)

```




\newpage


# Figure 4g - Density BMDC, Epitope, Concentration 10, Threshold 10


```{r echo=FALSE, fig.fullwidth=TRUE, fig.width=6, fig.height=4, }

density_table <- squares_master      %>% 
  filter(Cell_Type     == 'BMDC')    %>% 
  filter(Probe_Type    == 'Epitope') %>% 
  filter(Concentration == 10)        %>%
  filter(Adjuvant      == 'None')    %>% 
  filter(Threshold     == 10)

y_max         <- 70
y_ticks       <- 20

# Create the significance table
significance_bmdc_epitope_10 <- create_density_significance_table(density_table)

# Specify which pairs of probes to compare
signif <- list(c('1 Mono', '2 Mono'),
               c('2 Mono', '6 Mono'),
               c('1 Mono', '6 Mono'),
               c('1 Tri', '2 Tri'),
               c('2 Tri', '6 Tri'),
               c('1 Tri', '6 Tri'))

# Retrieve the significance values for these pairs
signif_value <- sapply(signif, function(x) get_significance(significance_bmdc_epitope_10, x[1], x[2]))

# Change to significance levels with stars
signif_num = as.numeric(signif_value)
for (i in 1:length(signif_value)) { 
  if (signif_num[i] > 0.05) {
    signif_value[i] = 'NS'
  } else if (signif_num[i] > 0.01) {
    signif_value[i] = '*'
  }
  else if (signif_num[i] > 0.001) {
    signif_value[i] = '**'
  }
  else if (signif_num[i] > 0.0001) {
     signif_value[i] = '***'
  }
  else {
    signif_value[i] = '****'
  }  
}

meds <- density_table %>% 
  group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
  summarize(med = round(median(Density), 1), .groups = 'keep')

bmdc_density <- density_table %>%
  ggplot(aes(x=Probe, y = Density, fill = Structure)) +
    geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
    geom_signif(comparisons = signif, annotations = signif_value, y_position = 35, step_increase = 0.2) +
    geom_text(data = meds, aes(y = med, label = round(med, 1)), size = 3, vjust = -0.5, color = "black") +
    geom_text(aes(label=paste0("n = ", after_stat(count))), y = -1, stat = 'count', colour = "black", size = 3) +
    labs(x = '',
         y = expression(events  / microm^2  /  sec (x1000))) +
    scale_y_continuous(limits = c(0, y_max), breaks=seq(0, y_max, y_ticks)) +
    scale_fill_manual(values=c(green_mono,
                               green_tri,
                               green_control)) +
    theme_light(base_size = 12) +
    theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))


bmdc_density  + 
  scale_x_discrete(labels = formatted_labels) +
  theme(axis.text.x = element_markdown(size = 9))

ggsave("./Figures/Traditional/Figure 4g.png", width = 6, height=4)
```

\newpage

# Figure ?? - Accepted squares



```{r, echo=FALSE, message=FALSE, fig.width=10, fig.height=6, fig.fullwidth=TRUE}

squares_master %>% 
  filter(Cell_Type %in% c('BMDC', 'MR-')) %>% 
  filter(Probe_Type == 'Simple') %>%
  filter(Adjuvant == 'None') %>% 
  filter(Structure %in% c('Mono', 'Tri')) %>%   
  filter(Probe %in% c('6 Mono', '1 Tri', '6 Tri')) %>% 
  ggplot(aes(x=Probe, fill= Structure)) +
    geom_bar() +
    geom_text(aes(label=sprintf('%d', after_stat(count))),
              stat ='count',
              nudge_y = 10,
              size= 6) +
    labs(title='', x='', y = 'Nr of accepted squares') +
    labs(caption='') +
    theme_light(base_size = 20) +
    theme(legend.position = "none") +
    #scale_y_continuous(limits=c(0, 50), breaks=seq(0, 50, 10)) +
    scale_fill_manual(values=c(green_mono,
                               green_tri,
                               green_control)) +
    facet_wrap(~ Cell_Type) 

ggsave("./Figures/Traditional/Figure 4c.png", width = 12, height=8)

```


