
---
title: "Overview of all experiment"
subtitle: 'Overview all experiments.Rmd'
fontfamily: sans
output:
  pdf_document:
    toc: yes
    toc_depth: 3
  html_document: default
  word_document: default
---

```{r Libraries, echo=FALSE, warning=FALSE, message=FALSE}

library(tidyverse)
library(readxl)
library(knitr)
library(ggsignif)
library(gridExtra)
library(kableExtra)
library(ggpmisc)

options(digits=2)

```


```{r Source, echo=FALSE, message=FALSE}

# Read in data

source('../Utility Code/Read Data - Regular Probes - Traditional.r')
source('../Utility Code/Colours.r')
source('../Utility Code/Significance.r')

```

```{r , echo=FALSE}

data_file_regular_20_02 <- '../../Data Integrated - v2/Paint Regular Probes - 20 squares - 2 DR'
data_file_regular_20_05 <- '../../Data Integrated - v2/Paint Regular Probes - 20 squares - 5 DR'
data_file_regular_20_10 <- '../../Data Integrated - v2/Paint Regular Probes - 20 squares - 10 DR'
data_file_regular_20_30 <- '../../Data Integrated - v2/Paint Regular Probes - 20 squares - 30 DR'

data_file_regular_30_02 <- '../../Data/Paint Regular Probes - 30 squares - 2 DR'
data_file_regular_30_05 <- '../../Data Integrated - v2/Paint Regular Probes - 30 squares - 5 DR'
data_file_regular_30_10 <- '../../Data Integrated - v2/Paint Regular Probes - 30 squares - 10 DR'
data_file_regular_30_30 <- '../../Data Integrated - v2/Paint Regular Probes - 30 squares - 30 DR'


data_file <- data_file_regular_30_02
manually_exclude <- FALSE
duration_exclude <- TRUE

```

```{r , echo=FALSE}


data <- read_data(data_file, 'Output', manually_exclude=manually_exclude, duration_exclude=duration_exclude)

squares_master <- data$squares_master
images_master  <- data$images_master



selection <- squares_master %>% 
  filter(Cell_Type   == 'CHOMR') %>% 
  filter(Probe_Type  == 'Epitope') %>%
  filter(Experiment_Date  == '240814')%>%
  filter(Adjuvant  == 'None')

```


\newpage


# Scatter plot of residence time vs density

```{r, echo=FALSE, fig.width=10, fig.height=4,}

tau_data <- squares_master %>% 
  filter(Cell_Type   == 'BMDC') %>% 
  filter(Probe_Type  == 'Epitope') %>%
  filter(Experiment_Date %in% c('240731', '240807'))%>%
  filter(Probe %in% c('1 Mono','2 Mono', '6 Mono', '1 Tri','2 Tri', '6 Tri','Control')) 
textsize = 8
tau_data %>%
  ggplot(mapping = aes(x=Tau, y=Density)) +
    geom_point(size = 0.0001) +
    labs(x='Average residence time (ms)', 
         y='Relative on-rate (events/µm/sec)') +
  theme_light(base_size = 13) +
  scale_x_continuous(limits = c(0, 410), breaks = seq(0, 400, by = 200)) +
  scale_y_continuous(limits = c(0, 35), breaks = seq(0, 35, by =10)) +
    facet_grid(Adjuvant ~ Probe, drop=TRUE) +
    theme(strip.text = element_text(size = textsize),
          axis.text = element_text(size = textsize))
ggsave("../../Figures/Traditional/Figure 5a.png", width = 10, height=4)

```

#For CHO-MR versus BMDC

```{r, echo=FALSE, fig.width=10, fig.height=4,}

tau_data <- squares_master %>% 
  filter(Cell_Type %in% c('BMDC', "CHOMR")) %>% 
  filter(Probe_Type  == 'Epitope') %>%
  filter(Probe %in% c('1 Mono','2 Mono', '6 Mono', '1 Tri','2 Tri', '6 Tri','Control'))
textsize = 8
tau_data %>%
  ggplot(mapping = aes(x=Tau, y=Density)) +
    geom_point(size = 0.0001) +
    labs(x='Average residence time (ms)', 
         y='Relative on-rate (events/µm/sec)') +
  theme_light(base_size = 13) +
  scale_x_continuous(limits = c(0, 410), breaks = seq(0, 400, by = 200)) +
    facet_grid(Cell_Type ~ Probe, drop=TRUE) +
    theme(strip.text = element_text(size = textsize),
          axis.text = element_text(size = textsize))
ggsave("../../Figures/Traditional/Figure 5d.png", width = 10, height=4)

```


```{r, echo=FALSE, fig.width=4, fig.height=2}

tau_data <- squares_master %>% 
  filter(Cell_Type %in% c('CHOMR')) %>% 
  filter(Threshold == 5 ) %>% 
  filter(Concentration == 1)%>%
  filter(Probe_Type  == 'Simple') %>%
  filter(Adjuvant == 'None')%>%
  filter(Probe %in% c('1 Tri', '6 Tri'))
textsize = 9
tau_data %>%
  ggplot(mapping = aes(x=Tau, y=Density)) +
    geom_point(size = 0.0001) +
    labs(x= expression(1/k[off] * " (ms)"), 
         y=expression( k[on] * " (evts/µm"^2 * "/sec)")) +
  theme_light(base_size = 9) +
  scale_x_continuous(limits = c(0, 410), breaks = seq(0, 400, by = 200)) +
  scale_y_continuous(limits = c(0, 300), breaks = seq(0, 300, by = 100)) +
    facet_grid( ~ Probe, drop=TRUE) +
    theme(strip.text = element_text(size = textsize),
          axis.text = element_text(size = textsize))
ggsave("../../Figures/Traditional/Figure 2hj.png", width = 4, height=2)

```
```{r, echo=FALSE, fig.width=4, fig.height=2}

tau_data <- squares_master %>% 
  filter(Cell_Type %in% c('BMDC')) %>% 
  filter(Threshold == 10 ) %>% 
  #filter(Concentration == 10)%>%
  filter(Probe_Type  == 'Simple') %>%
  filter(Adjuvant == 'None')%>%
  filter(Probe %in% c('1 Tri', '6 Tri'))
textsize = 9
tau_data %>%
  ggplot(mapping = aes(x=Tau, y=Density)) +
    geom_point(size = 0.0001) +
     labs(x= expression(1/k[off] * " (ms)"), 
         y=expression( k[on] * " (evts/µm"^2 * "/sec)")) +
  theme_light(base_size = 9) +
  scale_x_continuous(limits = c(0, 410), breaks = seq(0, 400, by = 200)) +
  scale_y_continuous(limits = c(0, 50), breaks = seq(0, 300, by = 10)) +
    facet_grid( ~ Probe, drop=TRUE) +
    theme(strip.text = element_text(size = textsize),
          axis.text = element_text(size = textsize))
ggsave("../../Figures/Traditional/Figure 2LM.png", width = 4, height=2)

```
\newpage

# Correlations table

```{r, echo=FALSE, fig.width=8, fig.height=8}


meds_comb <- function(data, probe_type, cell_type, adjuvant) {
  meds <- data %>%
    filter(Probe_Type == probe_type,
           Probe %in% c('1 Mono', '2 Mono', '6 Mono', '1 Tri', '2 Tri', '6 Tri', 'Control'),
           Cell_Type == cell_type,
           #Experiment_Date %in% c('240731', '240807'),
           Adjuvant == adjuvant) %>%
    group_by(Probe) %>%
    summarise(tau = median(Tau),
              density = median(Density),
              total_track_duration = sum(Total_Track_Duration),   # Median Total_Track_Duration
              avg_long_track_duration = median(Average_Long_Track_Duration))  # Median Average_Long_Track_Duration
  
  return(meds)
}

# Create a table with the Tau, Density, Total_Track_Duration, and Average_Long_Track_Duration for different condition combinations
combinations <- list(
  meds_comb(squares_master, 'Epitope', 'CHOMR', 'None'),
  meds_comb(squares_master, 'Epitope', 'BMDC',  'None'),
  meds_comb(squares_master, 'Epitope', 'CHOMR', 'CytD'),
  meds_comb(squares_master, 'Epitope', 'BMDC',  'CytD'),
  meds_comb(squares_master, 'Simple',  'CHOMR', 'None'),
  meds_comb(squares_master, 'Simple',  'BMDC',  'None')
)

# Merge the combinations into a single tibble
correlation_data <- reduce(combinations, left_join, by = 'Probe')

# Rename the columns to reflect the conditions, including the new medians
colnames(correlation_data) <- c('Probe', 
                                'Tau_E_CHOMR_None', 'Density_E_CHOMR_None', 'TotalTrack_E_CHOMR_None', 'AvgLongTrack_E_CHOMR_None',
                                'Tau_E_BMDC_None',  'Density_E_BMDC_None',  'TotalTrack_E_BMDC_None',  'AvgLongTrack_E_BMDC_None',
                                'Tau_E_CHOMR_CytD', 'Density_E_CHOMR_CytD', 'TotalTrack_E_CHOMR_CytD', 'AvgLongTrack_E_CHOMR_CytD',
                                'Tau_E_BMDC_CytD',  'Density_E_BMDC_CytD',  'TotalTrack_E_BMDC_CytD',  'AvgLongTrack_E_BMDC_CytD',
                                'Tau_S_CHOMR_None', 'Density_S_CHOMR_None', 'TotalTrack_S_CHOMR_None', 'AvgLongTrack_S_CHOMR_None',
                                'Tau_S_BMDC_None',  'Density_S_BMDC_None',  'TotalTrack_S_BMDC_None',  'AvgLongTrack_S_BMDC_None')

# Remove the combinations list to free up memory
rm(combinations)



# Add mean cycle for WT + MPLA and phagocytic index in BMDC and Kd derived SPR of simple glycans from Riera et al. SI

correlation_data <- correlation_data %>%
  mutate (mean_cycle = c(2.46, 1.97, 1.62, 1.72, 0.98, 0.39, 2.69),
          PI         = c(0.02494,	0.2383,	0.2811,	0.515,	0.7052,	0.3092,	0.01214),
          KdSPR      = c(100, 0 , 5.87, 4.62, 2.68, 3.14, 0 ))

#kable(correlation_data) %>% 
 # kable_styling(full_width = F) %>%
  #row_spec(0, angle = -90)

```


```{r, echo=FALSE, fig.width=6, fig.height=6}
# Epitope CHOMR vs BMDC none

# Simple vs Epitope for all probes except control
p1 <- correlation_data %>%
  filter(Probe != 'Control') %>%
  ggplot(mapping = aes(x=Tau_S_CHOMR_None, y=Tau_E_CHOMR_None)) +
    geom_point() +
    geom_text(aes(label = Probe), vjust = 0, nudge_y = 0.5) +
    scale_x_continuous(limits = c(40, 150), breaks = seq(0, 150, by = 25)) +
    scale_y_continuous(limits = c(40, 150), breaks = seq(0, 150, by = 25)) +
    geom_smooth(method = "lm", formula = y ~ x) +
    stat_poly_eq(aes(label = paste(after_stat(rr.label))), formula = y ~ x)

p1a <- correlation_data %>%
  filter(Probe != 'Control') %>%
  ggplot(mapping = aes(x=Density_S_CHOMR_None, y=Density_E_CHOMR_None)) +
    geom_point() +
    geom_text(aes(label = Probe), vjust = 0, nudge_y = 0.5) +
    #scale_x_continuous(limits = c(40, 150), breaks = seq(0, 150, by = 25)) +
    #scale_y_continuous(limits = c(40, 150), breaks = seq(0, 150, by = 25)) +
    geom_smooth(method = "lm", formula = y ~ x) +
    stat_poly_eq(aes(label = paste(after_stat(rr.label))), formula = y ~ x)

# Mean cycle vs KdSPR for all probes without control
p2 <- correlation_data %>%
  filter(Probe %in% c('1 Mono', '6 Mono', '1 Tri','2 Tri', '6 Tri')) %>% 
  ggplot(mapping = aes(x=mean_cycle, y=KdSPR)) +
    geom_point() +
    geom_text(aes(label=Probe), 
              nudge_x = c( 0,   0,   0,   0,   0,   0.1, 0.2),
              nudge_y = c(-0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1)) +
    scale_x_continuous(limits = c(-.5, 3.5), breaks = seq(-0.5, 3.5, by = 0.5)) +
    scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 25)) +
    geom_smooth(method = "lm", formula = y ~ x, color='red', fill='mistyrose') +
    stat_poly_eq(aes(label = paste(after_stat(rr.label))), 
                 label.x = 'left',
                 formula = y ~ x, 
                 color='red') 


# Mean cycle vs epitope tau CHOMR all probes
p3 <- correlation_data %>%
  ggplot(mapping = aes(x=mean_cycle, y=TotalTrack_E_BMDC_None)) +
    geom_point() +
    geom_text(aes(label=Probe), vjust = 0, nudge_y = 0.1) +
    #scale_y_continuous(limits = c(40, 100), breaks = seq(0, 150, by = 25)) +
    #scale_x_continuous(limits = c(-1, 3.5), breaks = seq(-1, 3.5, by = 1)) +
    geom_smooth(method = "lm", formula = y ~ x) +
    geom_smooth(data=correlation_data, method = "lm", formula = y ~ x, color='red', fill='mistyrose') +
    stat_poly_eq(aes(label = paste(after_stat(rr.label))), 
                 label.x = 'left',
                 formula = y ~ x, 
                 color='red')


# PI vs mean cycle, all probes
p4 <-correlation_data %>% 
  ggplot(mapping = aes(x=PI, y=mean_cycle)) +
    geom_point() +
    geom_text(mapping=aes(label=Probe), vjust = 0, nudge_y = 0.1) +
    geom_smooth(data=correlation_data, method = "lm", formula = y ~ x, color='red', fill='mistyrose') +
    stat_poly_eq(aes(label = paste(after_stat(rr.label))), 
                 label.x = 'left',
                 formula = y ~ x, 
                 color='red') +
    scale_x_continuous(limits = c(-.5, 1.5), breaks = seq(-0.5, 1.5, by = 0.5)) +
    scale_y_continuous(limits = c(-0, 3.5), breaks = seq(-1, 3.5, by = 1)) 
    

# BMDC Tau vs CHO-MR Tau (both with CytD)
p5 <- correlation_data %>%
  ggplot(mapping = aes(x=Tau_E_BMDC_CytD, y=Tau_E_CHOMR_CytD)) +
    geom_point() +
    geom_text(aes(label = Probe), vjust = 0, nudge_y = 0.5) +
    scale_x_continuous(limits = c(40, 150), breaks = seq(0, 150, by = 25)) +
    scale_y_continuous(limits = c(40, 150), breaks = seq(0, 150, by = 25)) +
    geom_smooth(method = "lm", formula = y ~ x) +
    stat_poly_eq(aes(label = paste(after_stat(rr.label))), formula = y ~ x)

# BMDC Tau vs CHO-MR Tau (both without adjuvant)
p6 <- correlation_data %>%
  ggplot(mapping = aes(x=Tau_E_BMDC_None, y=Tau_E_CHOMR_None)) +
    geom_point() +
    geom_text(aes(label = Probe), vjust = 0, nudge_y = 0.5) +
    scale_x_continuous(limits = c(40, 150), breaks = seq(0, 150, by = 25)) +
    scale_y_continuous(limits = c(40, 150), breaks = seq(0, 150, by = 25)) +
    geom_smooth(method = "lm", formula = y ~ x) +
    stat_poly_eq(aes(label = paste(after_stat(rr.label))), formula = y ~ x)

```


\newpage

# Correlation grid

```{r, echo=FALSE, fig.width=6, fig.height=9}

grid.arrange(p1, p2, p3, p4, p5, p6, ncol = 2)

```

```{r, echo=FALSE, fig.width=3, fig.height=2}

p4 + labs(x = 'Phagocytic Index (MFI)', y = 'Mean Cycles') + theme_light(base_size = 8)
ggsave("../../Figures/traditional/Figure 2b.png", width = 3, height=2)
```

```{r, echo=FALSE, fig.width=3, fig.height=2}

p2 + 
  xlab(expression(K[D]~(µM)~"derived from SPR")) + 
labs(y = 'Mean cycles (MFI)') + theme_light(base_size = 8)
ggsave("../../Figures/traditional/Figure 2spr.png", width = 3, height=2)
```
# Correlation between simple and epitope for CHO-MR

```{r, echo=FALSE, fig.width=3, fig.height=3}

p1 + labs(x = 'Glycocluster residence time (ms)', y = 'SLP glycocluster residence time (ms)') + theme_light(base_size = 9)
ggsave("../../Figures/traditional/Figure xb.png", width = 3, height=3)
```
```{r, echo=FALSE, fig.width=3, fig.height=3}

p1a + labs(x = 'Glycocluster residence time (ms)', y = 'SLP glycocluster residence time (ms)') + theme_light(base_size = 9)
ggsave("../../Figures/traditional/Figure xc.png", width = 3, height=3)
```
\newpage

# Correlation of Tau's of Epitope probes on CHO-MR and BMDC without Adjuvant



\newpage

# Correlation of Tau's on Epitope and Simple probes on CHO-MR without Adjuvant




\newpage

# Correlation of Phagocytic Index (on BMDC) with Epitope probe on CHO-MR witjout adjuvan


\newpage

# Correlation of Mean Cycle and PI


```{r, echo=FALSE, fig.width=8, fig.height=4}
# Correlations between mean_cycle with glycoPAINT derived Tau and Density in presence of CytD. Blue without and red is with CytD in one graph. 


#rescued from CHAT
#Density E CHOMR none vs CytD
x_data <- "Density_E_BMDC_CytD"
x2_data <- "Density_E_BMDC_None"
y_data <- "mean_cycle"

correlation_data_2Tri <- correlation_data %>% 
  filter(Probe != '2 Tri')
correlation_data_Control <- correlation_data %>% 
  filter(Probe != 'Control')

# Use the .data pronoun to reference the column names dynamically inside aes()
pCytD_density <- correlation_data %>%
  ggplot() +
  # Red points and regression for the first x_data (Density_E_CHOMR_CytD)
  geom_point(mapping = aes(x = .data[[x_data]], y = .data[[y_data]], shape = Probe), colour = 'red') + 
  geom_smooth(mapping = aes(x = .data[[x_data]], y = .data[[y_data]]), method = "lm", 
              formula = y ~ x, color = 'red', fill = 'mistyrose') +
  stat_poly_eq(mapping = aes(x = .data[[x_data]], y = .data[[y_data]], 
                             label = paste(after_stat(rr.label))), 
               label.x = 'right',
               formula = y ~ x, 
               color = 'red') +
  
  # Blue points and regression for the second x2_data (Density_E_CHOMR_None)
  geom_point(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]], shape = Probe), color = 'blue') + 
  geom_smooth(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]]), method = "lm", 
              formula = y ~ x, color = 'blue', fill = 'lightblue') +
  stat_poly_eq(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]], 
                             label = paste(after_stat(rr.label))), 
               label.x = 'left',
               formula = y ~ x, 
               color = 'blue') +
  
  # Remove legend for color
  theme(legend.position = "none") +
  scale_shape_manual(name = "Probe", values = c(0, 1, 2, 3, 4, 5, 6, 7)) +
  
  scale_x_continuous(limits = c(0, 10), breaks = seq(0, 20, by = 5)) +
  #scale_x_continuous(limits = c(40, 150), breaks = seq(0, 150, by = 25))+
  scale_y_continuous(limits = c(-0.5, 3.5), breaks = seq(-0.5, 3.5, by = 0.5)) +
  labs(y = 'T cell proliferation (MFI)', x = 'Density (evts/um/s)')
   

#Tau E CHOMR none vs CytD     
x_data <- "Tau_E_BMDC_CytD"
x2_data <- "Tau_E_BMDC_None"
y_data <- "mean_cycle"

correlation_data_2Tri <- correlation_data %>% 
  filter(Probe != '2 Tri')
correlation_data_Control <- correlation_data %>% 
  filter(Probe != 'Control')

# Use the .data pronoun to reference the column names dynamically inside aes()
pCytD_tau <- correlation_data %>%
  ggplot() +
  # Red points and regression for the first x_data (Density_E_CHOMR_CytD)
  geom_point(mapping = aes(x = .data[[x_data]], y = .data[[y_data]], shape = Probe), colour = 'red') + 
  geom_smooth(mapping = aes(x = .data[[x_data]], y = .data[[y_data]]), method = "lm", 
              formula = y ~ x, color = 'red', fill = 'mistyrose') +
  stat_poly_eq(mapping = aes(x = .data[[x_data]], y = .data[[y_data]], 
                             label = paste(after_stat(rr.label))), 
               label.x = 'right',
               formula = y ~ x, 
               color = 'red') +
  
  # Blue points and regression for the second x2_data (Density_E_CHOMR_None)
  geom_point(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]], shape = Probe), color = 'blue') + 
  geom_smooth(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]]), method = "lm", 
              formula = y ~ x, color = 'blue', fill = 'lightblue') +
  stat_poly_eq(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]], 
                             label = paste(after_stat(rr.label))), 
               label.x = 'left',
               formula = y ~ x, 
               color = 'blue') +
  
  scale_shape_manual(name = "Probe", values = c(0, 1, 2, 3, 4, 5, 6, 7)) +
  
  theme(legend.position = "none") +

  #scale_x_continuous(limits = c(0, 20), breaks = seq(0, 20, by = 5)) +
  scale_x_continuous(limits = c(40, 150), breaks = seq(0, 300, by = 25))+
  scale_y_continuous(limits = c(-0.5, 3.5), breaks = seq(-0.5, 3.5, by = 0.5)) +
  labs(y = 'T cell proliferation (MFI)', x = 'Average residence time (ms)')


merge <- grid.arrange(pCytD_tau_PI, pCytD_tau, ncol = 2)
ggsave( "../../Figures/traditional/Figure 4correlation.png", plot = merge, width = 8, height=4)
merge
```


\newpage

# Correlation of Mean Cycle and PI (with 2 Tri excluded)


```{r, echo=FALSE, fig.width=8, fig.height=4}

# Correlations between PI with glycoPAINT derived Tau and Density in presence of CytD. Blue without and red is with CytD in one graph. 


#rescued from CHAT
#Density E CHOMR none vs CytD
x_data <- "Density_E_BMDC_CytD"
x2_data <- "Density_E_BMDC_None"
y_data <- "PI"

correlation_data_2Tri <- correlation_data %>% 
  filter(Probe != '2 Tri')
correlation_data_Control <- correlation_data %>% 
  filter(Probe != 'Control')

# Use the .data pronoun to reference the column names dynamically inside aes()
pCytD_density <- correlation_data %>%
  ggplot() +
  # Red points and regression for the first x_data (Density_E_CHOMR_CytD)
  geom_point(mapping = aes(x = .data[[x_data]], y = .data[[y_data]]), colour = 'red') + 
  geom_smooth(mapping = aes(x = .data[[x_data]], y = .data[[y_data]]), method = "lm", 
              formula = y ~ x, color = 'red', fill = 'mistyrose') +
  stat_poly_eq(mapping = aes(x = .data[[x_data]], y = .data[[y_data]], 
                             label = paste(after_stat(rr.label))), 
               label.x = 'right',
               formula = y ~ x, 
               color = 'red') +
  
  # Blue points and regression for the second x2_data (Density_E_CHOMR_None)
  geom_point(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]]), color = 'blue') + 
  geom_smooth(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]]), method = "lm", 
              formula = y ~ x, color = 'blue', fill = 'lightblue') +
  stat_poly_eq(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]], 
                             label = paste(after_stat(rr.label))), 
               label.x = 'left',
               formula = y ~ x, 
               color = 'blue') +
  
  # Remove legend for color
  theme(legend.position = "none") +

  scale_x_continuous(limits = c(0, 20), breaks = seq(0, 20, by = 5)) +
  #scale_x_continuous(limits = c(40, 150), breaks = seq(0, 150, by = 25))+
  scale_y_continuous(limits = c(-.5, 2.5), breaks = seq(-0.5, 2, by = 0.5)) +
  labs(y = 'Phagocytic Index (MFI)', x = 'Density (evts/um/s)')
   

#Tau E CHOMR none vs CytD     
x_data <- "Tau_E_BMDC_CytD"
x2_data <- "Tau_E_BMDC_None"
y_data <- "PI"

correlation_data_2Tri <- correlation_data %>% 
  filter(Probe != '2 Tri')
correlation_data_Control <- correlation_data %>% 
  filter(Probe != 'Control')

# Use the .data pronoun to reference the column names dynamically inside aes()
pCytD_tau_PI <- correlation_data %>%
  ggplot() +
  # Red points and regression for the first x_data (Density_E_CHOMR_CytD)
  geom_point(mapping = aes(x = .data[[x_data]], y = .data[[y_data]]), colour = 'red') + 
  geom_smooth(mapping = aes(x = .data[[x_data]], y = .data[[y_data]]), method = "lm", 
              formula = y ~ x, color = 'red', fill = 'mistyrose') +
  stat_poly_eq(mapping = aes(x = .data[[x_data]], y = .data[[y_data]], 
                             label = paste(after_stat(rr.label))), 
               label.x = 'right',
               formula = y ~ x, 
               color = 'red') +
  
  # Blue points and regression for the second x2_data (Density_E_CHOMR_None)
  geom_point(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]]), color = 'blue') + 
  geom_smooth(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]]), method = "lm", 
              formula = y ~ x, color = 'blue', fill = 'lightblue') +
  stat_poly_eq(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]], 
                             label = paste(after_stat(rr.label))), 
               label.x = 'left',
               formula = y ~ x, 
               color = 'blue') +
  
  # Remove legend for color
#  theme(legend.position = "none") +

  #scale_x_continuous(limits = c(0, 20), breaks = seq(0, 20, by = 5)) +
  scale_x_continuous(limits = c(40, 150), breaks = seq(0, 150, by = 25))+
  scale_y_continuous(limits = c(-.5, 2.5), breaks = seq(-0.5, 2, by = 0.5)) +
  labs(y = 'Phagocytic Index (MFI)', x = 'Average residence time (ms)')

merge <- grid.arrange(pCytD_density, pCytD_tau_PI, ncol = 2)
merge

```


\newpage

# Correlation of Mean Cycle and glycoPAINT CytD kinetics


```{r, echo=FALSE, fig.width=8, fig.height=4}
# Correlations between mean_cycle with glycoPAINT derived Tau and Density in presence of CytD. Blue without and red is with CytD in one graph. 


#rescued from CHAT
#Density E CHOMR none vs CytD
x_data <- "Density_E_CHOMR_CytD"
x2_data <- "Density_E_CHOMR_None"
y_data <- "mean_cycle"

correlation_data_2Tri <- correlation_data %>% 
  filter(Probe != '2 Tri')
correlation_data_Control <- correlation_data %>% 
  filter(Probe != 'Control')

# Use the .data pronoun to reference the column names dynamically inside aes()
pCytD_density <- correlation_data %>%
  ggplot() +
  # Red points and regression for the first x_data (Density_E_CHOMR_CytD)
  geom_point(mapping = aes(x = .data[[x_data]], y = .data[[y_data]]), colour = 'red') + 
  geom_smooth(mapping = aes(x = .data[[x_data]], y = .data[[y_data]]), method = "lm", 
              formula = y ~ x, color = 'red', fill = 'mistyrose') +
  stat_poly_eq(mapping = aes(x = .data[[x_data]], y = .data[[y_data]], 
                             label = paste(after_stat(rr.label))), 
               label.x = 'right',
               formula = y ~ x, 
               color = 'red') +
  
  # Blue points and regression for the second x2_data (Density_E_CHOMR_None)
  geom_point(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]]), color = 'blue') + 
  geom_smooth(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]]), method = "lm", 
              formula = y ~ x, color = 'blue', fill = 'lightblue') +
  stat_poly_eq(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]], 
                             label = paste(after_stat(rr.label))), 
               label.x = 'left',
               formula = y ~ x, 
               color = 'blue') +
  
  # Remove legend for color
  theme(legend.position = "none") +

  scale_x_continuous(limits = c(0, 20), breaks = seq(0, 20, by = 5)) +
  #scale_x_continuous(limits = c(40, 150), breaks = seq(0, 150, by = 25))+
  scale_y_continuous(limits = c(-0.5, 3.5), breaks = seq(-0.5, 3.5, by = 0.5)) +
  labs(y = 'T cell proliferation (MFI)', x = 'Density (evts/um/s)')
   

#Tau E CHOMR none vs CytD     
x_data <- "Tau_E_CHOMR_CytD"
x2_data <- "Tau_E_CHOMR_None"
y_data <- "mean_cycle"

correlation_data_2Tri <- correlation_data %>% 
  filter(Probe != '2 Tri')
correlation_data_Control <- correlation_data %>% 
  filter(Probe != 'Control')

# Use the .data pronoun to reference the column names dynamically inside aes()
pCytD_tau <- correlation_data %>%
  ggplot() +
  # Red points and regression for the first x_data (Density_E_CHOMR_CytD)
  geom_point(mapping = aes(x = .data[[x_data]], y = .data[[y_data]]), colour = 'red') + 
  geom_smooth(mapping = aes(x = .data[[x_data]], y = .data[[y_data]]), method = "lm", 
              formula = y ~ x, color = 'red', fill = 'mistyrose') +
  stat_poly_eq(mapping = aes(x = .data[[x_data]], y = .data[[y_data]], 
                             label = paste(after_stat(rr.label))), 
               label.x = 'right',
               formula = y ~ x, 
               color = 'red') +
  
  # Blue points and regression for the second x2_data (Density_E_CHOMR_None)
  geom_point(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]]), color = 'blue') + 
  geom_smooth(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]]), method = "lm", 
              formula = y ~ x, color = 'blue', fill = 'lightblue') +
  stat_poly_eq(mapping = aes(x = .data[[x2_data]], y = .data[[y_data]], 
                             label = paste(after_stat(rr.label))), 
               label.x = 'left',
               formula = y ~ x, 
               color = 'blue') +
  
  # Remove legend for color
  theme(legend.position = "none") +

  #scale_x_continuous(limits = c(0, 20), breaks = seq(0, 20, by = 5)) +
  scale_x_continuous(limits = c(40, 150), breaks = seq(0, 150, by = 25))+
  scale_y_continuous(limits = c(-0.5, 3.5), breaks = seq(-0.5, 3.5, by = 0.5)) +
  labs(y = 'T cell proliferation (MFI)', x = 'Average residence time (ms)')

merge <- grid.arrange(pCytD_density, pCytD_tau, ncol = 2)
merge
```
