---
title: "Tau of Epitope probes on CHO-MR and BMDC"
subtitle: 'CHO-MR and BMDC - Epitope.Rmd'
fontfamily: sans
output:
  pdf_document:
    toc: yes
    toc_depth: 3
  html_document: default
  word_document: default
---

```{r Libraries, echo=FALSE, warning=FALSE, message=FALSE}

library(tidyverse)
library(readxl)
library(knitr)
library(ggsignif)
library(gridExtra)

```


```{r Source, echo=FALSE, message=FALSE}

source('../Utility Code/Read Data - Regular Probes - Single.r')
source('../Utility Code/Colours.r')
source('../Utility Code/Significance.R')

```

```{r , echo=FALSE}

data_file_regular_20_02 <- '../../Data Integrated/Paint Regular Probes - 20 squares - 2 DR'
data_file_regular_20_05 <- '../../Data Integrated/Paint Regular Probes - 20 squares - 5 DR'
data_file_regular_20_10 <- '../../Data Integrated/Paint Regular Probes - 20 squares - 10 DR'
data_file_regular_20_30 <- '../../Data Integrated/Paint Regular Probes - 20 squares - 30 DR'

data_file_regular_30_02 <- '../../Data/Paint Regular Probes - 30 squares - 2 DR'
data_file_regular_30_05 <- '../../Data Integrated/Paint Regular Probes - 30 squares - 5 DR'
data_file_regular_30_10 <- '../../Data Integrated/Paint Regular Probes - 30 squares - 10 DR'
data_file_regular_30_30 <- '../../Data Integrated/Paint Regular Probes - 30 squares - 30 DR'

data_file <- data_file_regular_30_02
manually_exclude <- FALSE
duration_exclude <- TRUE

```


```{r , echo=FALSE}

data <- read_data(data_file, 'Output', manually_exclude=manually_exclude, duration_exclude=duration_exclude)

squares_master <- data$squares_master
images_master  <- data$images_master

```


```{r , echo=FALSE}

# Add the structure informatiin to images_master\
images_master$Probe_Copy  <- images_master$Probe
images_master$Probe_Copy  <- as.character(images_master$Probe_Copy)
images_master$Probe_Copy[images_master$Probe_Copy == 'Control'] <- '0 Control'
images_master             <- separate(images_master, Probe_Copy, into = c("Valency", "Structure"), sep = " ")
images_master$Structure   <- factor(images_master$Structure,   levels = c('Mono', 'Bi', 'Tri', 'Control'))

```


```{r , echo=FALSE}

images_master <- images_master %>%
  filter(Tau > 0)

```


\newpage

# Tau of Epitope probes on CHO-MR and BMDC

Description of the figure:

* Cell types:         CHO-MR and BMDC
* Probe type:         Epitope
* Adjuvant:           None

For Tau it is ok to take all concentrations and all quality threshold values

\hfill\break
\hfill\break




```{r echo=FALSE, tau_significance_violin}

generate_tau_plot <- function(tau_table, y_limit) {
  
  # Create the significance table
  significance_tau <- create_tau_significance_table(tau_table)
  
  # Specify which pairs of probes you want to compare
  signif = list(c('1 Mono', '2 Mono'),
                c('2 Mono', '6 Mono'),
                c('1 Mono', '6 Mono'),
                c('1 Tri', '2 Tri'),
                c('2 Tri', '6 Tri'),
                c('1 Tri', '6 Tri'))
  
  # Retrieve the previously calculated significance for these pairs
  signif_value  <- c(get_significance(significance_tau, '1 Mono', '2 Mono'),
                     get_significance(significance_tau, '2 Mono', '6 Mono'),
                     get_significance(significance_tau, '1 Mono', '6 Mono'),
                     get_significance(significance_tau, '1 Tri', '2 Tri'),
                     get_significance(significance_tau, '2 Tri', '6 Tri'),
                     get_significance(significance_tau, '1 Tri', '6 Tri'))
  
  signif_num = as.numeric(signif_value)
  for (i in 1:length(signif_value)) {
    if (signif_num[i] > 0.05) {
      signif_value[i] = 'NS'
    }
    else if (signif_num[i] > 0.01) {
      signif_value[i] = '*'
    }
    else if (signif_num[i] > 0.001) {
      signif_value[i] = '**'
    }
    else if (signif_num[i] > 0.0001) {
      signif_value[i] = '***'
    }
    else {
      signif_value[i] = '****'
    }  
  }
  
  meds <- tau_table %>% 
    group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
    summarize(med = round(median(Tau), 0), .groups = 'keep')
  
  #define text size
  basesize = 5
  
  plot_data <- tau_table %>%
    ggplot(aes(x=Probe, y = Tau, fill = Structure)) + 
      # geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
      geom_boxplot(width = 0.9, show.legend = FALSE) +
      geom_jitter(width = 0.3) +
      geom_signif(comparisons = signif, annotations = signif_value, y_position = 450, step_increase = 0.1, textsize = 4) +
      geom_text(data = meds, aes(y = med, label = round(med, 2)), size = 1, vjust = -0.5, color = "black") +
      geom_text(aes(label=paste0("n = ", after_stat(count))), y = -10, stat = 'count', colour = "black", size = 1) + 
      labs(x = '', 
           y = 'Average residence time (ms)',
           caption = '') +
      scale_y_continuous(limits = c(-50, y_limit), breaks=seq(0, y_limit, 200)) +
      scale_fill_manual(values=c(green_mono,
                                 green_tri,
                                 green_control)) +
      theme_light(base_size = basesize) +
      theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
      theme(text=element_text(size=basesize),        #change font size of all text
            axis.text=element_text(size=basesize),   #change font size of axis text
            axis.title=element_text(size=basesize))  #change font size of axis titles
  

  return (plot_data)
}

```

\hfill\break
\hfill\break
 
## Without significance

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=10, fig.width=24}

tau_table <- images_master  %>% 
  filter(Cell_Type %in% c('CHOMR', 'BMDC')) %>% 
  filter(Probe_Type == 'Simple') %>%
  filter(Probe %in% c('1 Mono', '2 Mono', '6 Mono', '1 Tri', '2 Tri', '6 Tri', 'Control'))%>%
  filter(Adjuvant   == 'None')

y_limit <- 400

meds <- tau_table %>% 
  group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
  summarize(med = round(median(Tau), 0), .groups = 'keep')
  
tau_table %>%
  ggplot(aes(x=Probe, y = Tau, fill = Structure)) + 
    # geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
    geom_boxplot(width = 0.3, show.legend = FALSE) +
    geom_jitter(width = 0.3) +
    geom_text(data = meds, aes(y = med, label = round(med, 2)), size = 5, vjust = -0.5, color = "black") +
    geom_text(aes(label=paste0("n = ", after_stat(count))), y = -10, stat = 'count', colour = "black", size = 3) + 
    labs(x = '', 
         y = 'Average residence time (ms)',
         caption = '') +
    scale_y_continuous(limits = c(-50, y_limit), breaks=seq(0, y_limit, 100)) +
    scale_fill_manual(values=c(green_mono,
                               green_tri,
                               green_control)) +
    theme_light(base_size = 20) +
    theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
    facet_wrap( ~ Cell_Type, drop = TRUE)


```
\newpage

## With significance

### CHO-MR

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=10, fig.width=12}

# ----------------------------------------------------------------------------
# For Tau it is ok to take all concentrations and all quality threshold values
# ----------------------------------------------------------------------------

# Generate the CHO-MR plot 
tau_table <- images_master  %>% 
  filter(Cell_Type  == 'CHOMR') %>% 
  filter(Probe_Type == 'Epitope') %>%
  filter(Adjuvant   == 'None')
p_cho <- generate_tau_plot (tau_table, 650)

p_cho
ggsave("./Figures/Single/Figure 4d.png", width = 6, height=4)
```


\hfill\break
\hfill\break

### BMDC

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=10, fig.width=12}
# Generate the BMDC plot 
tau_table <- images_master  %>% 
  filter(Cell_Type  == 'BMDC') %>% 
  filter(Probe_Type == 'Epitope') %>%
  filter(Adjuvant   == 'None')
p_bmdc <- generate_tau_plot (tau_table, 800)


p_bmdc
ggsave("./Figures/Single/Figure 4e.png", width = 12, height=8)
#ggsave("./Figuresaaa/Single/Figure 4e.png", width = 12, height=8)

```




\newpage

# Density CHO-MR, Epitope, 5, 5

Description of the figure:

-   Cell type: CHO-MR
-   Probe type: Epitope
-   Concentration: 5
-   Threshold: 5
-   Adjuvant: None

To meaningfully compare density you really need to have the same Concentration and Quality threshold

\hfill\break


## Without Significance - Traditional

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=10, fig.width=24}
density_table <- squares_master      %>% 
  filter(Cell_Type     == 'CHOMR')   %>% 
  filter(Probe_Type    == 'Epitope') %>% 
  filter(Concentration == 5)         %>%
  filter(Adjuvant      == 'None')    %>% 
  filter(Threshold     == 5)

y_max         <- 120
y_ticks       <- 20

meds <- density_table %>% 
  group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
  summarize(med = round(median(Density), 1), .groups = 'keep')

density_table %>%
  ggplot(aes(x=Probe, y = Density, fill = Structure)) +
    geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
    # geom_boxplot(width = 0.9, show.legend = FALSE) +
    # geom_jitter(width = 0.3) +
    geom_text(data = meds, aes(y = med, label = round(med, 1)), size = 5, vjust = -0.5, color = "black") +
    geom_text(aes(label=paste0("n = ", after_stat(count))), y = -2, stat = 'count', colour = "black", size = 3) +
    labs(x = '',
         y = expression(events  / microm^2  /  sec (x1000))) +
    scale_y_continuous(limits = c(0, y_max), breaks=seq(0, y_max, y_ticks)) +
    scale_fill_manual(values=c(green_mono,
                               green_tri,
                               green_control)) +
    theme_light(base_size = 20) +
    theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

```

## Without Significance - Single

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=10, fig.width=24}
density_table <- images_master      %>% 
  filter(Cell_Type     == 'CHOMR')   %>% 
  filter(Probe_Type    == 'Epitope') %>% 
  filter(Concentration == 5)         %>%
  filter(Adjuvant      == 'None')    %>% 
  filter(Threshold     == 5)

y_max         <- 20
y_ticks       <- 5

meds <- density_table %>% 
  group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
  summarize(med = round(median(Density), 1), .groups = 'keep')

density_table %>%
  ggplot(aes(x=Probe, y = Density, fill = Structure)) +
    # geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
    geom_boxplot(width = 0.9, show.legend = FALSE) +
    geom_jitter(width = 0.3, show.legend = FALSE) +
    geom_text(data = meds, aes(y = med, label = round(med, 1)), size = 5, vjust = -0.5, color = "black") +
    geom_text(aes(label=paste0("n = ", after_stat(count))), y = 0, stat = 'count', colour = "black", size = 3) +
    labs(x = '',
         y = expression(events  / microm^2  /  sec (x1000))) +
    scale_y_continuous(limits = c(0, y_max), breaks=seq(0, y_max, y_ticks)) +
    scale_fill_manual(values=c(green_mono,
                               green_tri,
                               green_control)) +
    theme_light(base_size = 20) +
    theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

```


\hfill\break
\hfill\break

## With significance

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=10, fig.width=24}

density_table <- squares_master      %>% 
  filter(Cell_Type     == 'CHOMR')   %>% 
  filter(Probe_Type    == 'Epitope') %>% 
  filter(Concentration == 5)         %>%
  filter(Adjuvant      == 'None')    %>% 
  filter(Threshold     == 5)

y_max         <- 120
y_ticks       <- 20

# Create the significance table
significance_cho_epitope_5 <- create_density_significance_table(density_table)

signif = list(c('2 Mono', '6 Mono'),
              c('2 Tri',  '6 Tri'),
              c('2 Mono', '2 Tri'),
              c('2 Mono', '6 Tri'))

signif_value  <- c(get_significance(significance_cho_epitope_5, '2 Mono', '6 Mono'),
                   get_significance(significance_cho_epitope_5, '2 Tri', '6 Tri'),
                   get_significance(significance_cho_epitope_5, '2 Mono', '2 Tri'),
                   get_significance(significance_cho_epitope_5, '2 Mono', '6 Tri'))

signif_num = as.numeric(signif_value)
for ( i in 1:length(signif_value)) {
  if (signif_num[i] > 0.05) {
    signif_value[i] = 'NS'
  }
}

meds <- density_table %>% 
  group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
  summarize(med = round(median(Density), 1), .groups = 'keep')

cho_mr_density <- density_table %>%
  ggplot(aes(x=Probe, y = Density, fill = Structure)) +
    geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
    geom_signif(comparisons = signif, annotations = signif_value, y_position = 65, step_increase = 0.2) +
    geom_text(data = meds, aes(y = med, label = round(med, 1)), size = 5, vjust = -0.5, color = "black") +
    geom_text(aes(label=paste0("n = ", after_stat(count))), y = -2, stat = 'count', colour = "black", size = 3) +
    labs(x = '',
         y = expression(events  / microm^2  /  sec (x1000))) +
    scale_y_continuous(limits = c(0, y_max), breaks=seq(0, y_max, y_ticks)) +
    scale_fill_manual(values=c(green_mono,
                               green_tri,
                               green_control)) +
    theme_light(base_size = 20) +
    theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))


cho_mr_density 
ggsave("./Figures/Single/Figure 4f.png", width = 12, height=8)
```




\newpage

# Density BMDC, Epitope, 10, 10


Description of the figure:

-   Cell type:     BMDC
-   Probe type:    Epitope
-   Concentration: 10
-   Threshold:     10
-   Adjuvant:      None

To meaningfully compare density you really need to have the same Concentration and Quality threshold

\hfill\break


## Without Significance - Traditional

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=10, fig.width=24}

density_table <- squares_master      %>% 
  filter(Cell_Type     == 'BMDC')    %>% 
  filter(Probe_Type    == 'Epitope') %>% 
  filter(Concentration == 10)        %>%
  filter(Adjuvant      == 'None')    %>% 
  filter(Threshold     == 10)

y_max         <- 40
y_ticks       <- 20

meds <- density_table %>% 
  group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
  summarize(med = round(median(Density), 1), .groups = 'keep')

density_table %>%
  ggplot(aes(x=Probe, y = Density, fill = Structure)) +
    geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width', drop=FALSE) +
    geom_text(data = meds, aes(y = med, label = round(med, 1)), size = 5, vjust = -0.5, color = "black") +
    geom_text(aes(label=paste0("n = ", after_stat(count))), y = -2, stat = 'count', colour = "black", size = 3) +
    labs(x = '',
         y = expression(events  / microm^2  /  sec (x1000))) +
    #scale_y_continuous(limits = c(0, y_max), breaks=seq(0, y_max, y_ticks)) +
    scale_fill_manual(values=c(green_mono,
                               green_tri,
                               green_control)) +
    theme_light(base_size = 20) +
    theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

```


## Without Significance - Single

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=10, fig.width=24}

density_table <- images_master      %>% 
  filter(Cell_Type     == 'BMDC')    %>% 
  filter(Probe_Type    == 'Epitope') %>% 
  filter(Concentration == 10)        %>%
  filter(Adjuvant      == 'None')    %>% 
  filter(Threshold     == 10)

y_max         <- 10
y_ticks       <- 5

meds <- density_table %>% 
  group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
  summarize(med = round(median(Density), 1), .groups = 'keep')

density_table %>%
  ggplot(aes(x=Probe, y = Density, fill = Structure)) +
    #geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
    geom_boxplot(width = 0.9, show.legend = FALSE) +
    geom_jitter(width = 0.3, show.legend = FALSE) +
    geom_text(data = meds, aes(y = med, label = round(med, 1)), size = 5, vjust = -0.5, color = "black") +
    geom_text(aes(label=paste0("n = ", after_stat(count))), y = 0, stat = 'count', colour = "black", size = 5) +
    labs(x = '',
         y = expression(events  / microm^2  /  sec (x1000))) +
    scale_y_continuous(limits = c(0, y_max), breaks=seq(0, y_max, y_ticks)) +
    scale_fill_manual(values=c(green_mono,
                               green_tri,
                               green_control)) +
    theme_light(base_size = 20) +
    theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

```


\hfill\break
\hfill\break

## With significance

```{r echo=FALSE, fig.fullwidth=TRUE, fig.height=10, fig.width=24}

density_table <- squares_master      %>% 
  filter(Cell_Type     == 'BMDC')    %>% 
  filter(Probe_Type    == 'Epitope') %>% 
  filter(Concentration == 10)        %>%
  filter(Adjuvant      == 'None')    %>% 
  filter(Threshold     == 10)

y_max         <- 40
y_ticks       <- 20

# Create the significance table
significance_bmdc_epitope_10 <- create_density_significance_table(density_table)

signif = list(c('2 Mono', '6 Mono'),
              c('2 Tri',  '6 Tri'),
              c('2 Mono', '2 Tri'),
              c('2 Mono', '6 Tri'))

signif_value  <- c(get_significance(significance_bmdc_epitope_10, '2 Mono', '6 Mono'),
                   get_significance(significance_bmdc_epitope_10, '2 Tri', '6 Tri'),
                   get_significance(significance_bmdc_epitope_10, '2 Mono', '2 Tri'),
                   get_significance(significance_bmdc_epitope_10, '2 Mono', '6 Tri'))

signif_num = as.numeric(signif_value)
for ( i in 1:length(signif_value)) {
  if (signif_num[i] > 0.05) {
    signif_value[i] = 'NS'
  }
}

meds <- density_table %>% 
  group_by(Probe, Cell_Type, Probe_Type, Structure) %>%
  summarize(med = round(median(Density), 1), .groups = 'keep')

bmdc_density <- density_table %>%
  ggplot(aes(x=Probe, y = Density, fill = Structure)) +
    geom_violin(width = 0.9, show.legend = FALSE, trim = TRUE, scale='width') +
    geom_signif(comparisons = signif, annotations = signif_value, y_position = 25, step_increase = 0.2) +
    geom_text(data = meds, aes(y = med, label = round(med, 1)), size = 5, vjust = -0.5, color = "black") +
    geom_text(aes(label=paste0("n = ", after_stat(count))), y = -1, stat = 'count', colour = "black", size = 5) +
    labs(x = '',
         y = expression(events  / microm^2  /  sec (x1000))) +
    scale_y_continuous(limits = c(0, y_max), breaks=seq(0, y_max, y_ticks)) +
    scale_fill_manual(values=c(green_mono,
                               green_tri,
                               green_control)) +
    theme_light(base_size = 20) +
    theme(panel.border = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))


bmdc_density
ggsave("./Figures/Single/Figure 4g.png", width = 12, height=8)
```

\newpage

# Accepted squares

## Simple

```{r, echo=FALSE, message=FALSE, fig.width=10, fig.height=6, fig.fullwidth=TRUE}

squares_master %>% 
  filter(Cell_Type %in% c('BMDC', 'MR-')) %>% 
  filter(Probe_Type == 'Simple') %>%
  filter(Adjuvant == 'None') %>% 
  filter(Structure %in% c('Mono', 'Tri')) %>%   
  filter(Probe %in% c('6 Mono', '1 Tri', '6 Tri')) %>% 
  ggplot(aes(x=Probe, fill= Structure)) +
    geom_bar() +
    geom_text(aes(label=sprintf('%d', after_stat(count))),
              stat ='count',
              nudge_y = 10,
              size= 6) +
    labs(title='', x='', y = 'Nr of accepted squares') +
    labs(caption='') +
    theme_light(base_size = 20) +
    theme(legend.position = "none") +
    #scale_y_continuous(limits=c(0, 50), breaks=seq(0, 50, 10)) +
    scale_fill_manual(values=c(green_mono,
                               green_tri,
                               green_control)) +
    facet_wrap(~ Cell_Type) 

ggsave("./Figures/Single/Figure 4c.png", width = 12, height=8)

```


## Epitope

```{r, echo=FALSE, message=FALSE, fig.width=10, fig.height=6, fig.fullwidth=TRUE}

squares_master %>% 
  filter(Cell_Type %in% c('BMDC', 'MR-')) %>% 
  filter(Probe_Type == 'Epitope') %>%
  filter(Adjuvant == 'None') %>% 
  ggplot(aes(x=Probe, fill= Structure)) +
    geom_bar() +
    geom_text(aes(label=sprintf('%d', after_stat(count))),
              stat    ='count',
              nudge_y = 10,
              size    = 6) +
    labs(title='', x='', y = 'Nr of accepted squares') +
    labs(caption='') +
    theme_light(base_size = 20) +
    theme(legend.position = "none") +
    scale_fill_manual(values=c(green_mono,
                               green_tri,
                               green_control)) +
    facet_wrap(~ Cell_Type) 

```